% !TEX program = xelatex

\documentclass{resume}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=blue,citecolor=green,urlcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yaming Huang}

\contactInfo{\href{mailto:yumminhuang@gmail.com}{yumminhuang@gmail.com}}
{(+86) 12345678901}
{\href{https://github.com/yumminhuang}{yumminhuang}}

%
%Education
%

\section{Academic Experience}

\datedsubsection{\textbf{Northeastern University}, Boston, MA}{Sept. 2013 --- Dec. 2015}
\datedline{\textit{M.S.} in Computer Science}{GPA: 3.875/4.0}
\textbf{Selected Curriculum Projects}
\begin{itemize}
\item \datedline{Managing Software Development Project}{Sept. --- Dec. 2015}
\begin{itemize}
\item Built a JAX-RS website --- WHAM (What Happened Around Me) using Jersey and Tomcat;
\item Managed software development progress by Scrum methodology;
\item Used Jira to track issues and Confluence to manage documents.
\end{itemize}

\item \datedline{MapReduce Project}{Sept. --- Dec. 2015}
\begin{itemize}
\item Analyze San Francisco crime incidents and predict crime category by na\"{i}ve bayesian algorithm
\item Run Hadoop and Spark programs on AWS EMR
\end{itemize}

\item \datedline{Computer Networking Projects}{Jan. --- Apr. 2014}
\begin{itemize}
\item \textit{Raw Sockets} --- Built TCP/IP stack using Python raw sockets
\item \textit{Roll Your Own CDN} --- Built a simplified Content Delivery Network using AWS EC2
\end{itemize}

\item \datedline{Database Project}{Sept. --- Dec. 2013}
\begin{itemize}
\item Built Odata service(RESTful APIs for accessing database) over MySQL using JPA
\end{itemize}
\end{itemize}

\datedsubsection{\textbf{Jinan University}, Guangzhou, China}{Sept. 2009 --- Jul. 2013}
\datedline{\textit{B.E.} in Softerware Engineering}{GPA: 84.6/100}
\textbf{Thesis}
\begin{itemize}
\item \textit{Visual Fault Localization Tool for Java Multi-threaded Program}
\begin{itemize}
\item Dynamic fault-localization tool to locate concurrent faults in multi-threaded Java programs
\item Using Soot to analyze Java byte code and instrument Java programs
\end{itemize}
\end{itemize}

%
%Experience
%

%\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
%\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
%Brief introduction: xxx
%\begin{itemize}
%  \item Implemented xxx feature
%  \item Optimized xxx 5\%
%  \item xxx
%\end{itemize}

\section{Professional Experience}
\datedsubsection{\textbf{BitSight}, Cambridge, MA}{Jan. --- Aug. 2015}
\role{Operation Engineer Co-Op}{}
\begin{itemize}
%\item Architected and built a Security Updates Management Tool for Ubuntu Cluster using Sensu to report and leveraging Jenkins to build
\item Architected and built a Security Updates Management Tool for Ubuntu Cluster based on Sensu Alerts for reporting and leveraging Jenkins to build
%\item Contributed to CI automation by grabbing test results from Jenkins builds and posting to BitBucket
\item Contributed to CI automation by improving python framework to grab test reporting data from Jenkins Builds and summarize that information as a comment on BitBucket PullRequests
\item Added improvements to open source projects (automated-ebs-snapshots, BitBucket API, sensu-plugin, etc)
\item Automated workflows for dumping/restoring test minified database based on Jenkins and Fabric
\item Implemented and rolled out proof of concepts for logging management(ELK, Logentries, Sumologic)
, writing chef code to deploy these solutions, mocking up dashboards and prototyping example searches of high-value queries
\end{itemize}

\datedsubsection{\textbf{Locately}, Boston, MA}{Jul. --- Aug. 2014}
\role{Back-end Software Engineer Intern}{}
\begin{itemize}
\item Implemented Auto Scaling on AWS, a feature reducing operations costs by \$3000/year
\item Wrote Apache access log monitor in EC2 instances to collect access statistics to AWS CloudWatch
\item Rewrote test code allowing parallel testing to speed up API test execution by 17\%
\end{itemize}

\datedsubsection{\textbf{Aston University}, Birmingham, United Kingdom}{Mar. --- Apr. 2012}
\role{Software Developer Intern}{}
\begin{itemize}
\item Developed an Eclipse plug-in called \textit{Scenario Capture} which can automatically generate JUnit test cases in GUI
\item Tested code by JUnit
\end{itemize}

%
%Programming Skills
%

\section{Technical Skills}
\begin{description}[style=nextline,leftmargin=8em,topsep=1pt,parsep=0.5ex]
  \item[Languages] Python, Java, Ruby, Shell, Racket
  \item[Tools] Chef, Docker, Git, Jenkins, Jira, SQL, UML
  \item[Frameworks] Django, Hadoop
  \item[Methodologies] Agile, Scrum
\end{description}

%
%Honors & Awards
%

%
% Publications
%

%\section {Publication}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


% \section{Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
% \item \faHome:  \url{http://yumminhuang.github.io}
% \item \faLinkedin: \url{https://www.linkedin.com/pub/yaming-huang/5b/932/6a0}
% \end{itemize}

\end{document}
