\documentclass{resume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Yaming Huang}
{\href{mailto:yumminhuang@gmail.com}{yumminhuang@gmail.com}}
{123-456-7890}
{\href{https://github.com/yumminhuang}{yumminhuang}}
{\href{https://www.linkedin.com/in/yaming-huang-6a09325b}{Yaming Huang}}
{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Professional Experience}

\begin{body}
	\company{Thoughtworks}
	{Shanghai, China}
	{Sept. 2019 --- Now}
	{Senior Consultant}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item \project{Legacy Payment Gateway in Australian}{DevOps Tech Lead}{Feb. 2020 --- Now}
		\begin{itemize}[noitemsep,topsep=0pt]
			\item Based on PCI standards, identified and fixed security issues in payment gateways, and passed PCI DSS audits.
			\item Built an automated AWS security scanning tool, based on CIS Benchmark, to repair security issues for 3 AWS accounts.
		\end{itemize}
		\item \project{System of Singapore Goverment}{DevOps Specialist}{Sept. 2019 --- Dec. 2019}
		\begin{itemize}[noitemsep,topsep=0pt]
			\item Built a deployment platform based on GoCD in the government's private cloud to achieve automated deployment while meeting the government's strict security compliance.
			\item Improved monitoring and log collection to achieve comprehensive monitoring and log diagnosis of infrastructure, microservices and 3-party services.
		\end{itemize}
		\item Participated in the pre-sales, to provide solution support for car sales, system operation and maintenance, \textit{etc}.
	\end{itemize}
	\company{Thoughtworks}
	{Beijing, China}
	{Aug. 2017 --- Sept. 2019}
	{Consultant}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item \project{Mobile Platform for an Automobile 4S Stores in China Area}{DevOps Tech Lead}{}
		\begin{itemize}[noitemsep,topsep=0pt]
			\item Provided DevOps and SRE support in the $100$-person team, participate in cloud architecture design, infrastructure setup, continuous delivery, monthly release, environmental operation and maintenance, logging and monitoring, \textit{etc}.
			\item Ran 5 environments(Production and DR included) on Azure. Used Terraform to manage $100+$ VMs and other Azure services. Completed Azure cross-region migration and DR setup.
			\item Migrated container orchestrator platform from Rancher to Kubernetes for 4 environments within 4 months.
			\item Leveraged GoCD to manage more than 120 continuous delivery pipelines through \textit{Pipeline as Code} and Kubernetes \textit{Elastic Agent}.
			\item Used Ansible and Saltstack to manage VM configurations to ensure the consistency and rapid change for the 5 environments.
			\item Set up Prometheus to monitor infrastructures, micro-services and 3rd-party services.
			\item Set up Elasticsearch clusters to provide logging diagnostics, which collects and stores 30GB logs per day.
		\end{itemize}
	\end{itemize}
\end{body}

\begin{body}
	\company{LeEco Zhixin}
	{Beijing, China}
	{Jul. 2016 --- Jul. 2017}
	{DevOps Engineer}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Managed the distributed Gerrit clusters, which hosts about 1TB codebase, for providing the code host service to over 1500 developers around the world
		\item Established a real-time data analysis platform based on ELK and Superset that collecting data from Jenkins and Gerrit to provide data analysis and decision support
		\item Developed Ansible playbooks for Gerrit and ELK, implementing automated deployment and configuration
		\item Built a continuous delivery pipeline for PHP project based on Jenkinsfile
	\end{itemize}
\end{body}

\begin{body}
	\company{BitSight}
	{Cambridge, MA}
	{Jan. --- Aug. 2015}
	{Operation Engineer Co-Op}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Architected and built a Security Updates Management Tool for Ubuntu Cluster based on Sensu Alerts for reporting and leveraging Jenkins to build
		\item Contributed to CI automation by improving python framework to grab test reporting data from Jenkins Builds and summarize that information as a comment on BitBucket Pull Requests
		\item Added improvements to open source projects (automated-ebs-snapshots, BitBucket-api, sensu-plugin, etc)
		\item Automated workflows for dumping/restoring test minified database based on Jenkins and Fabric
		\item Implemented and rolled out proof of concepts for logging management(ELK, Logentries, Sumologic), writing chef code to deploy these solutions, mocking up dashboards and prototyping example searches of high-value queries
	\end{itemize}
\end{body}

\begin{body}
	\company{Locately}
	{Boston, MA}
	{July --- Aug. 2014}
	{Back-end Software Engineer Intern}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Implemented Auto Scaling on AWS, a feature reducing operations costs by \$3000/year
		\item Wrote Apache access log monitor in EC2 instances to collect access statistics to AWS CloudWatch
		\item Rewrote test code allowing parallel testing to speed up API test execution by 17\%
	\end{itemize}
\end{body}

%\begin{body}
%	\company{Aston University}
%   {Birmingham, United Kingdom}
%	{Mar. --- Apr. 2012}
%	{Software Developer Intern}
%	\begin{itemize}[noitemsep,topsep=0pt]
%		\item Developed an Eclipse plug-in called \textit{Scenario Capture} which can automatically
%			  generate JUnit test cases in GUI
%		\item Tested code by JUnit
%	\end{itemize}
%\end{body}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Academic Experience}

\begin{body}
	\school{\textbf{Northeastern University}, Boston, MA}
	{Sept. 2013 --- May. 2016}
	{Master of Science in Computer Science}
	{GPA: 3.875/4.00}
	% \textbf{Selected Curriculum Projects}
	% \begin{itemize}
	% \item \project{Managing Software Development Project}{Sept. --- Dec. 2015}
	% \begin{itemize}
	% 	\item Built a JAX-RS website --- WHAM (What Happened Around Me) using Jersey and Tomcat
	% 	\item Setup a continuous deployment pipeline on Jenkins
	% 	\item Managed software development progress by Scrum, with using Jira to track issues and Confluence to manage documents
	% \end{itemize}

	% \item \project{MapReduce Project}{Oct. --- Dec. 2015}
	% \begin{itemize}
	% 	\item Analyzed San Francisco crime incidents and predict crime category by na\"{i}ve bayesian algorithm
	% 	\item Ran Hadoop and Spark programs on AWS EMR
	% \end{itemize}

	% \item \project{Computer Networking Projects}{Jan. --- Apr. 2014}
	% \begin{itemize}
	% 	\item \textit{Raw Sockets} --- Built TCP/IP stack using Python raw socket
	% 	\item \textit{Roll Your Own CDN} --- Built a simplified Content Delivery Network on AWS EC2
	% \end{itemize}

	% \item \project{Datebase Project}{Sept. --- Dec. 2013}
	% \begin{itemize}
	% 	\item Built Odata service(RESTful APIs for accessing database) over MySQL using JPA
	% \end{itemize}

	% \end{itemize}
\end{body}

\begin{body}
	\school{\textbf{Jinan University}, Guangzhou, CHINA}
	{Sept. 2009 --- July 2013}
	{Bachelor of Engineering in Software Engineering}
	{GPA: 84.6/100}
	% \textbf{Thesis}
	% \begin{itemize}
	% \item \textit{Visual Fault Localization Tool for Java Multi-threaded Program}
	% \begin{itemize}
	% 	\item Implement a dynamic fault-localization tool to locate concurrent faults in multi-threaded Java programs
	% 	\item Using Soot to analyze Java byte code and SWT to build a GUI
	% \end{itemize}
	% \end{itemize}
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Technical Skills}

\begin{body}
\begin{description}[style=nextline,leftmargin=8em,topsep=1pt]
	\item[Languages] Python, Shell, Java, Ruby
	\item[Tools] Ansible, Saltstack, Terraform, Consul, Gerrit, GoCD, Jenkins
	\item[Cloud] Azure, AWS
	\item[Monitoring] Prometheus, Elastic Stack, Grafana
\end{description}
\end{body}


%\smallskip

% \newpage{} % uncomment this line if you want to force a new page


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%\header{Selected Publications}

%\begin{body}
%	Seth Holloway. ``\textbf{Writing Resumes in LaTeX},'' in \emph{Proceedings of the Mind of Seth Holloway}. 2011.\\
%	\smallskip
%	Seth Holloway, Andrea Holloway. ``\textbf{Accent Modification Rules},'' in \emph{Proceedings of Fun}. 2008.\\
%\end{body}
%
%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
%\header{AWARDS AND HONORS}

%\begin{body}
%	\textbf{Third Class University Scholarship}, Jinan University \hfill{} 2011\\
%	\smallskip
%	\textbf{Third Class Graduating Student Scholarship},  Jinan University \hfill{} 2013
%\end{body}

\header{Professional Certificates}

\begin{body}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item AWS Certified Solutions Architect (Professional)
		\item Certified Kubernetes Administrator
	\end{itemize}
\end{body}

%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Interests
%\header{INTERESTS}
%\begin{body}
%	Photography, Travel, Soccer
%\end{body}

\end{document}
