\documentclass{newresume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Yaming Huang}
{\href{mailto:yumminhuang@gmail.com}{yumminhuang@gmail.com}}
{123-456-7890}
{\href{https://github.com/yumminhuang}{yumminhuang}}
{\href{https://www.linkedin.com/in/yaming-huang-6a09325b}{Yaming Huang}}
{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Professional Experience}

\begin{body}
	\school{\textbf{LeEco Zhixin}, Beijing, China}
	{Jul. 2016 --- Present}
	{DevOps Engineer}
	{}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Managed the distributed Gerrit cluster, which hosts about 1TB codebase, for providing the code host service to over 1500 developers around the world
		\item Established a real-time data analysis platform that collecting data from Jenkins build and Gerrit cluster to provide data analysis and decision support
		\item Developed an Ansible playbook for Gerrit cluster, implementing automated deployment and configuration
	\end{itemize}
\end{body}

\begin{body}
	\school{\textbf{BitSight}, Cambridge, MA}
	{Jan. --- Aug. 2015}
	{Operation Engineer Co-Op}
	{}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Architected and built a Security Updates Management Tool for Ubuntu Cluster based on Sensu Alerts for reporting and leveraging Jenkins to build
		\item Contributed to CI automation by improving python framework to grab test reporting data from Jenkins Builds and summarize that information as a comment on BitBucket PullRequests
		\item Added improvements to open source projects (automated-ebs-snapshots, BitBucket-api, sensu-plugin, etc)
		\item Automated workflows for dumping/restoring test minified database based on Jenkins and Fabric
		\item Implemented and rolled out proof of concepts for logging management(ELK, Logentries, Sumologic), writing chef code to deploy these solutions, mocking up dashboards and prototyping example searches of high-value queries
	\end{itemize}
\end{body}

\begin{body}
	\school{\textbf{Locately}, Boston, MA}
	{July --- Aug. 2014}
	{Back-end Software Engineer Intern}
	{}
	\begin{itemize}[noitemsep,topsep=0pt]
		\item Implemented Auto Scaling on AWS, a feature reducing operations costs by \$3000/year
		\item Wrote Apache access log monitor in EC2 instances to collect access statistics to AWS CloudWatch
		\item Rewrote test code allowing parallel testing to speed up API test execution by 17\%
	\end{itemize}
\end{body}

%\begin{body}
%	\school{\textbf{Aston University}, Birmingham, United Kingdom}
%	{Mar. --- Apr. 2012}
%	{Software Developer Intern}
%	{}
%	\begin{itemize}[noitemsep,topsep=0pt]
%		\item Developed an Eclipse plug-in called \textit{Scenario Capture} which can automatically
%			  generate JUnit test cases in GUI
%		\item Tested code by JUnit
%	\end{itemize}
%\end{body}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Academic Experience}

\begin{body}
	\school{\textbf{Northeastern University}, Boston, MA}
	{Sept. 2013 --- Dec. 2015}
	{Master of Science in Computer Science}
	{GPA: 3.875/4.00}
	\textbf{Selected Curriculum Projects}
	\begin{itemize}
	\item \project{Managing Software Development Project}{Sept. --- Dec. 2015}
	\begin{itemize}
		\item Built a JAX-RS website --- WHAM (What Happened Around Me) using Jersey and Tomcat
		\item Setup a continuous deployment pipeline on Jenkins
		\item Managed software development progress by Scrum, with using Jira to track issues and Confluence to manage documents
	\end{itemize}

	\item \project{MapReduce Project}{Oct. --- Dec. 2015}
	\begin{itemize}
		\item Analyzed San Francisco crime incidents and predict crime category by na\"{i}ve bayesian algorithm
		\item Ran Hadoop and Spark programs on AWS EMR
	\end{itemize}

	\item \project{Computer Networking Projects}{Jan. --- Apr. 2014}
	\begin{itemize}
		\item \textit{Raw Sockets} --- Built TCP/IP stack using Python raw socket
		\item \textit{Roll Your Own CDN} --- Built a simplified Content Delivery Network on AWS EC2
	\end{itemize}

	\item \project{Datebase Project}{Sept. --- Dec. 2013}
	\begin{itemize}
		\item Built Odata service(RESTful APIs for accessing database) over MySQL using JPA
	\end{itemize}

	\end{itemize}
\end{body}

\begin{body}
	\school{\textbf{Jinan University}, Guangzhou, CHINA}
	{Sept. 2009 --- July 2013}
	{Bachelor of Engineering in Software Engineering}
	{GPA: 84.6/100}
	\textbf{Thesis}
	\begin{itemize}
	\item \textit{Visual Fault Localization Tool for Java Multi-threaded Program}
	\begin{itemize}
		\item Implement a dynamic fault-localization tool to locate concurrent faults in multi-threaded Java programs
		\item Using Soot to analyze Java byte code and SWT to build a GUI
	\end{itemize}
	\end{itemize}
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Technical Skills}

\begin{description}[style=nextline,leftmargin=8em,topsep=1pt]
	\item[Languages] Python, Java, Ruby, Shell, Racket
	\item[Tools] Ansible, Chef, Docker, Git, Gerrit, Jenkins, Jira, MySQL, Postgres, Superset
	\item[Frameworks] AWS, Elastic Stack, Django, Hadoop
	\item[Methodologies] Agile, Scrum
\end{description}

%\smallskip

% \newpage{} % uncomment this line if you want to force a new page


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%\header{Selected Publications}

%\begin{body}
%	Seth Holloway. ``\textbf{Writing Resumes in LaTeX},'' in \emph{Proceedings of the Mind of Seth Holloway}. 2011.\\
%	\smallskip
%	Seth Holloway, Andrea Holloway. ``\textbf{Accent Modification Rules},'' in \emph{Proceedings of Fun}. 2008.\\
%\end{body}
%
%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
%\header{AWARDS AND HONORS}

%\begin{body}
%	\textbf{Third Class University Scholarship}, Jinan University \hfill{} 2011\\
%	\smallskip
%	\textbf{Third Class Graduating Student Scholarship},  Jinan University \hfill{} 2013
%\end{body}

%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Interests
%\header{INTERESTS}
%\begin{body}
%	Photography, Travel, Soccer
%\end{body}

\end{document}
